### 2017-04-02 paper/oopsla17-submission/discussion.tex
Wes pass over rest of text

\paragraph{User-Defined Types}
Probably the single biggest limitation of our technique is that we have
features for specific data and type constructors.
%
Anything our models learn about errors made with the |::| constructor or
the |list| type cannot easily be translated to new, user-defined
datatypes the model has never encountered.
%
We can attempt to mitigate this to some extent by adding generic
syntactic features for data constructors and match expressions, but it
remains to be seen how much these help \ES{TODO: UW data!}.
%
Furthermore, there is no obvious analog for transferring knowledge to
new type constructors, which we have seen are both more compact and
helpful.

@@

\paragraph{Additional Features}
There are a number of other features that could improve the model's
ability to localize errors, that would be easier to add than
user-defined types.
%
For example, each occurrence of a variable knows only its type and the
immediate context in which it occurs, but it may be helpful to know
about \emph{other} occurrences of the same variable.
%
If a variable is generally used in the context of a |float| but has a
single occurrence in the context of an |int|, it seems likely that the
latter occurrence (or context) is to blame.
%
Similarly, arguments to a function application are not aware of the
typing constraints imposed on them by the function (and vice versa),
they only know that they are occurring in the context of an application
and the type of the application itself.
%
Finally, \emph{n-grams} on the token stream have proven effective for
probabilistic modeling of programming languages, we may find that they
aid in our task as well.
%
For example, if the observed tokens in an expression diverge from the
n-gram model's predictions, that indicates that there is something
unusual about the program at that point, and it may signal an error.

>>>>

\paragraph{User-Defined Types}
Probably the single biggest limitation of our technique is that we have
(a finite set of) features for specific data and type constructors.
%
Anything our models learn about errors made with the |::| constructor or
the |list| type cannot easily be translated to new, user-defined
datatypes the model has never encountered.
%
We can mitigate this, to some extent, by adding generic
syntactic features for data constructors and match expressions, but it
remains to be seen how much these help \ES{TODO: UW data!}.
%
Furthermore, there is no obvious analog for transferring knowledge to
new type constructors, which we have seen are both more compact and
helpful.

@@

\paragraph{Additional Features}
There are a number of other features that could improve the model's
ability to localize errors, that would be easier to add than
user-defined types.
%
For example, each occurrence of a variable knows only its type and the
immediate context in which it occurs, but it may be helpful to know
about \emph{other} occurrences of the same variable.
%
If a variable is generally used in the context of a |float| but has a
single occurrence in the context of an |int|, it seems likely that the
latter occurrence (or context) is to blame.
%
Similarly, arguments to a function application are not aware of the
typing constraints imposed on them by the function (and vice versa),
they only know that they are occurring in the context of an application
and the type of the application itself.
%
Finally, \emph{n-grams} on the token stream have proven effective for
probabilistic modeling of programming languages~\cite{FIXME,FIXME}, we may
find that they aid in our task as well.
%
For example, if the observed tokens in an expression diverge from the
n-gram model's predictions, that indicates that there is something
unusual about the program at that point, and it may signal an error.

### 2017-04-02 paper/oopsla17-submission/related.tex
Wes pass over rest of text

\subsection{Fault Localization}
Given a defect, \emph{fault localization} is the task of identifying
``suspicious'' program elements (\eg lines, statements) that are likely
implicated in the defect (\ie that should be changed to fix the defect)
%
--- thus, type error localization can be viewed as an instance of fault
localization.
%
The best-known fault localization technique is likely Tarantula, which
uses a simple mathematical formula based on measured information from
dynamic normal and buggy runs~\citep{Jones2002-us}.
%
Other similar approaches, including those of \citet{Chen2002-qz} and
\citet{Abreu2006-fn,Abreu2007-mu} consider alternate features of
information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey.
%
While some researchers have approached such fault localization with an
eye toward optimality (\eg \citet{Yoo2013-rw} determine optimal
coefficients), in general such fault localization approaches are limited
by their reliance on either running tests or including relevant
features.
%
For example, Tarantula-based techniques require a normal and a buggy run
of the program.
%
By contrast, we consider incomplete programs with type errors that may
not be executed in any standard sense.
%
Similarly, the features available influence the classes of defects that
can be localized.
%
A fault localization scheme based purely on control flow features
will have difficulty with cross-site scripting or SQL code injection
attacks, which follow the same control flow path on normal and buggy
runs (differing only in the user-supplied data).
%
Our feature set is comprised entirely of syntactic and typing features,
a natural choice for modeling type errors, but it would likely not
generalize to other types of defects.

>>>>

\subsection{Fault Localization}
Given a defect, \emph{fault localization} is the task of identifying
``suspicious'' program elements (\eg lines, statements) that are likely
implicated in the defect (\ie that should be changed to fix the defect)
%
--- thus, type error localization can be viewed as an instance of fault
localization.
%
The best-known fault localization technique is likely Tarantula, which
uses a simple mathematical formula based on measured information from
dynamic normal and buggy runs~\citep{Jones2002-us}.
%
Other similar approaches, including those of \citet{Chen2002-qz} and
\citet{Abreu2006-fn,Abreu2007-mu} consider alternate features of
information or refined formulae and generally obtain more precise
results; see \citet{Wong2009-pd} for a survey.
%
While some researchers have approached such fault localization with an
eye toward optimality (\eg \citet{Yoo2013-rw} determine optimal
coefficients), in general such fault localization approaches are limited
by their reliance on either running tests or including relevant
features.
%
For example, Tarantula-based techniques require a normal and a buggy run
of the program.
%
By contrast, we consider incomplete programs with type errors that may
not be executed in any standard sense.
%
Similarly, the features available influence the classes of defects that
can be localized.
%
For example, a fault localization scheme based purely on control flow features
will have difficulty with cross-site scripting or SQL code injection
attacks, which follow the same control flow path on normal and buggy
runs (differing only in the user-supplied data).
%
Our feature set is comprised entirely of syntactic and typing features,
a natural choice for modeling type errors, but it would likely not
generalize to other types of defects.
